A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-11-19 paper/paper.tex
paper: macro cleanup, NFC

% The label, since we're including twice
\newcommand*{\lab}{}

@@

The definition of the type of a $n$-truncated $\nu$-set is in turn described in \ref{tab:core}. In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$. The type $\fullframe$ represents a matching object. It is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$. The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in \ref{tab:faces}, and this restriction operator is in turn defined using the auxiliary definitions of $\restrl$ and $\restrc$.

@@

\renewcommand*{\lab}{tab:coind}
\input{tab-coind.tex}

@@

\renewcommand*{\lab}{tab:core}
\input{tab-core.tex}

% Drop the universe letter in fullframe for all remaining tables
\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
\renewcommand*{\lab}{tab:frames}
\input{tab-frames.tex}

@@

\renewcommand*{\lab}{tab:faces}
\input{tab-faces-ett.tex}

@@

\renewcommand*{\lab}{tab:coh}
\input{tab-coh-ett.tex}

@@

% Insert fulltab:faces and fulltab:coh, after overriding macros to make
% everything but the universe letter explicit.
\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
\renewcommand*{\lab}{fulltab:faces}
\renewcommand{\thetable}{4'}
\input{tab-faces.tex}
\renewcommand*{\lab}{fulltab:coh}
\renewcommand{\thetable}{5'}
\input{tab-coh.tex}

>>>>

@@

The definition of the type of a $n$-truncated $\nu$-set is in turn described in table \ref{tab:core}. In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$. The type $\fullframe$ represents a matching object. It is recursively defined in table \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$. The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table \ref{tab:faces}, and this restriction operator is in turn defined using the auxiliary definitions of $\restrl$ and $\restrc$.

@@

\def\lab{tab:coind}
\input{tab-coind.tex}

@@

\def\lab{tab:core}
\input{tab-core.tex}

% Drop the universe letter in fullframe for all remaining tables
\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
\def\lab{tab:frames}
\input{tab-frames.tex}

@@

\def\lab{tab:faces}
\input{tab-faces-ett.tex}

@@

\def\lab{tab:coh}
\input{tab-coh-ett.tex}

@@

% Insert fulltab:faces and fulltab:coh, after overriding macros to make
% everything but the universe letter explicit.
\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
\def\lab{fulltab:faces}
\renewcommand{\thetable}{4'}
\input{tab-faces.tex}
\def\lab{fulltab:coh}
\renewcommand{\thetable}{5'}
\input{tab-coh.tex}
